SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-11 docs/questioning.tex
first steps in conclusions

% In the last 15 years there are numerous mechanisms that have
% been developed to detect one or more of the attacks mentioned
% above. However, the majority of them are not used in practice.
% This is due to the following reasons:
% a) the mechanisms have not been extensively tested in terms
% of accuracy,
% b) are hard to deploy because they require many modifications
% either on the client-side, the server-side, or both,
% c) they add significant overhead, and
% d) can be bypassed by attackers that know how they work.
% The motivation behind this research is to systematize
% and analyze previously proposed protection mechanisms.
% In this way we can highlight the advantages
% and disadvantages of each mechanism, enlist them
% into different categories, and see how they compare to each other.

\begin{itemize}
\item Cite~\cite{HNSHS12,DKH14}.
\item We believe that our research may facilitate researchers
or practitioners who would like to use one of the
aforementioned mechanisms and researchers who would like
to build new ones. Especially in the second case,
researchers can utilize our exploitation model as a
starting point to develop their approach.
\item We believe that forming a
standard way to test such mechanisms in terms
of accuracy and computational performance
would be one of the reasons of adopting them.
\end{itemize}

>>>>

Despite many approaches that have been developed,
application attacks based on source code injection
have been consistenly present for the last 15 years,
and it appears that they will continue to be.
Attackers seem to find new ways to introduce
source code to applications by using a variety of
languages and techniques~\cite{HNSHS12,DKH14}.
Meanwhile, duirng the last decade, there are
numerous mechanisms that have been developed to
detect one or more of such attacks. However,
% even if
% some of them share characteristics with supported frameworks
% like Mozilla's Content Security
% Policy\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}
% ({\sc csp}) and Google
% Caja\footnote{\url{https://code.google.com/p/google-caja/}}~\cite{M06},
the majority of them are not used in practice.

% This is due to the following reasons:
% a) the mechanisms have not been extensively tested in terms
% of accuracy,
% b) are hard to deploy because they require many modifications
% either on the client-side, the server-side, or both,
% c) they add significant overhead, and
% d) can be bypassed by attackers that know how they work.
% The motivation behind this research is to systematize
% and analyze previously proposed protection mechanisms.
% In this way we can highlight the advantages
% and disadvantages of each mechanism, enlist them
% into different categories, and see how they compare to each other.

\begin{itemize}
\item We believe that our research may facilitate researchers
or practitioners who would like to use one of the
aforementioned mechanisms and researchers who would like
to build new ones. Especially in the second case,
researchers can utilize our exploitation model as a
starting point to develop their approach.
\item We believe that forming a
standard way to test such mechanisms in terms
of accuracy and computational performance
would be one of the reasons of adopting them.
\end{itemize}
